### 2023-12-11 main.tex
''

At each vertex site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ {\color{blue} denotes the number of particles of species $a\in \{1,\ldots,N-1\}$, while the component $n_{N}^{x}$ denotes the number of holes at site $x$.} On each vertex we {\color{blue} allow a total maximal number of particles $\nu\in \mathbb{N}$}. {\color{blue} In the following we introduce the indices denoted by lowercase letters $a,b,c,d,k\in \{1,\ldots,N-1\}$ when only particles are taken into account. Moreover, we introduce the indices denoted by uppercase letters $A,B,C,D,K\in\{1,\ldots,N\}$ when we also consider the hole, that we recall is denoted by $N$. The link between the two indices is given by 

>>>>

At each vertex site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ {\color{blue} denotes the number of particles of species $a\in \{1,\ldots,N-1\}$, while the component $n_{N}^{x}$ denotes the number of holes at site $x$.} On each vertex we {\color{blue} allow a total maximal number of particles $\nu\in \mathbb{N}$}. {\color{blue} In the following we introduce the indices denoted by lowercase letters (for instance $a,b,c,d,k\in \{1,\ldots,N-1\}$) when only particles are taken into account. Moreover, we introduce the indices denoted by uppercase letters (for instance $A,B,C,D,K\in\{1,\ldots,N\}$) when we also consider the hole, that we recall is denoted by $N$. The link between the two indices is given by 
